%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MCM/ICM LaTeX Template %%
%% 2022 MCM/ICM           %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{left=1in,right=0.75in,top=1in,bottom=1in}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% 感觉这里在定义宏变量Problem和Team
\newcommand{\Problem}{C}
\newcommand{\Team}{2218530}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{newtxtext}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{newtxmath} % must come after amsXXX
\usepackage[pdftex]{graphicx}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{lastpage}

\lhead{Team \Team}
\rhead{}
\cfoot{}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}{Definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % 开始paper
\begin{document}   

% 设置文章头
\graphicspath{{.}}  % 图片文件夹路径名
\DeclareGraphicsExtensions{.pdf, .jpg, .tif, .png}  % 图片文件的后缀
\thispagestyle{empty}   % 这一页的页面格式，empty表示没有页眉页脚
\vspace*{-16ex}
% 设置表格，加中间线并写队名啥的……
\centerline{\begin{tabular}{*3{c}}
	\parbox[t]{0.3\linewidth}{\begin{center}\textbf{Problem Chosen}\\ \Large \textcolor{red}{\Problem}\end{center}}
	& \parbox[t]{0.3\linewidth}{\begin{center}\textbf{2022\\ MCM/ICM\\ Summary Sheet}\end{center}}
	& \parbox[t]{0.3\linewidth}{\begin{center}\textbf{Team Control Number}\\ \Large \textcolor{red}{\Team}\end{center}}	\\
	\hline
\end{tabular}}

%%%%%%%%%%% Begin Summary %%%%%%%%%%%
\begin{center}
Use this template to begin typing the first page (summary page) of your electronic report. This \newline
template uses a 12-point Times New Roman font. Submit your paper as an Adobe PDF \newline
electronic file (e.g. 1111111.pdf), typed in English, with a readable font of at least 12-point type.	\\[2ex]
Do not include the name of your school, advisor, or team members on this or any page.	\\[2ex]
Papers must be within the 25 page limit.	\\[2ex]
Be sure to change the control number and problem choice above.	\\
You may delete these instructions as you begin to type your report here. 	\\[2ex]
Follow us @COMAPMath on Twitter or COMAPCHINAOFFICIAL on Weibo for the \newline
most up to date contest information.

\end{center}
%%%%%%%%%%% End Summary %%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage  % 新的一页
\setcounter{page}{1}    % 设置这一页是第1页
\pagestyle{fancy}%fancyhdr宏包新增的页面风格
% 设置目录
\tableofcontents
\rhead{Page \thepage\ of \pageref{LastPage}}    %当前页 of 总页数

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 开始正文
%\part{Introduction}
%\chapter{Background}
\section{Introduction}
\subsection{Background}
% 背景

\subsection{Statment of the problem}
% 问题重述


\rhead{Page \thepage\ of \pageref{LastPage}}

\end{document}

\end




